Chasing Speeders: Analyzing Toronto’s 2023 Speeding Trends in School Zones”

### 2024-12-07 paper/paper.qmd
fix wording, add map info

## Interactive website
An interactive Leaflet map was developed to visualize the locations of speed cameras and Watch Your Speed signs using a 500-meter spatial join. This map provides an accessible view of enforcement coverage across Toronto, allowing users to explore geographic distributions and the density of speed enforcement infrastructure. Markers represent the locations of speed cameras and signs showing the spatial reach of current traffic safety measures in school areas. Please see the website [here](https://karenrni.github.io/leaflet-web-map/).

>>>>

## Interactive website
An interactive Leaflet map was developed to visualize the locations of speeding incidents based on the speed cameras and Watch Your Speed signs using a 500-meter spatial join. This map provides an accessible view of enforcement coverage across Toronto, allowing users to explore geographic distributions and the density of speed enforcement infrastructure, as well as the speed limit, observed Speed (numeric midpoint of the speed bin), volume of incidents and ward number. Markers represent the locations of speed cameras and signs showing the spatial reach of current traffic safety measures in school areas. Please see the website [here](https://karenrni.github.io/leaflet-web-map/).
